%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry} % Document margins

\name{Chenxi Li} % Your name
\address{ +44 (0)~$\cdot$~7000~$\cdot$~000000 \\ surname.lastname@email.com} % Your phone number and email

\begin{document}

    %----------------------------------------------------------------------------------------
    %	WORK EXPERIENCE SECTION
    %----------------------------------------------------------------------------------------

    \begin{rSection}{Experience}

        \begin{rSubsection}{Citi}{Jul. 2015 - Aug. 2017}{FX Developer, FX STIRT Desk}{London, UK}
            \item Developing a \textbf{Storm} cluster in Java for calculating \textbf{Real-time Risk} (RTR), PAA and P\&L
            for STIRT product,closely working with traders and quants
            \item Architected parallelisation refactors over the project, improved the scalability of RTR system,
            by increasing the processors in Storm Topology
            \item Leading the role in implementing quant calculation modules within system,
            helping improve the quant library used across Citi rates business
            \item Saved 70\% of startup time and calculation time by implementing a new system architect
            \item Led the project on rolling out Realtime Risk System for CEEMEA desk
            \item Optimising side systems, RESTful service, MongoDB, and performance tuning, to support core functions
        \end{rSubsection}

        %------------------------------------------------
        \begin{rSubsection}{Citi}{Aug. 2013 - Jun. 2015}{Graduate Associate, Citi Institutional Client Group}{London, UK}
            \item Piloted the project using Zing JVM for better performance,
            involved in daily e-trading business support, in Citi Equity Electronic Execution team as first rotation
            \item Developed a green-field real-time monitoring system with Storm and CEP to capture trading engine's events,
            including incidents, anomalies, and vital system information
            \item Explored and implemented projects in various pieces of technologies, such as Esper CEP,
            Storm Engine, D3, and ZeroMQ, to process, analyse and visualize hybrid of trading and hardware data
            \item Solo developer responsible for a web-based gift logging system to host business activities,
            with full stack JavaScript technology, including MongoDB, Node.js, Meteor, and Bootstrap
            \item Gained good overview on operations in back office from investment bank, especially in instruction and settlement,
            in Citi Middle Office Technology as second rotation
            \item Completed intensive training, gained essential investment banking knowledge and relevant technical information
            associated with current system, and networked with senior international staff
        \end{rSubsection}

        %------------------------------------------------
        \begin{rSubsection}{Citicorp Software and Technology Services Co., Ltd}{Aug 2012}
        {\textbf{Tech. Infrastructure Support}, Citi Tech. Infrastructure}{Shanghai, China}
            \item Involved in daily network system maintenance, resolved network problems with local branches,
            coordinated communication of errors and updates with Singapore office
            \item Assisted in replacing current voice system with Cisco Call Management System,
            consulted with external vendors and communicated with local branches
        \end{rSubsection}

        %------------------------------------------------
        \begin{rSubsection}{The People's Bank of China}{Jul. 2009 - Aug. 2009}
        {\textbf{Summer Analyst}, Department of Currency, Credit and Statistics}{Nanjing, China}
            \item Synthesized local banks' financial information, and extracted business procedures
            \item Collected and analysed market information for weekly research reports
            \item Assigned to Bank of China as part of internship, involved in daily operations,
            and served clients with various background
        \end{rSubsection}

    \end{rSection}

    %----------------------------------------------------------------------------------------
    %	EDUCATION SECTION
    %----------------------------------------------------------------------------------------

    \begin{rSection}{Education}
        \begin{rSubsection}{\textbf{Imperial College London}} {Sep. 2012 - Sep. 2013}{}{}
            \item MSc (Hons) in Computing (Computational Management Science)
            \item Computational Finance, Operations Research, Machine Learning, Intelligent Data and Probabilistic Inference,
            Stimulation and Modelling, and Computing for Optimal Decision
        \end{rSubsection}

        \begin{rSubsection}{\textbf{University of Liverpool}} {Aug. 2008 - Jul. 2012}{}{}
            \item BSc (Hons) in Artificial Intelligence with \textbf{First Class Honours}
            \item Awarded XJTLU Scholarship
            \item 1st Prize Winner in XJTLU Mathematical Modelling Competition (1st among 50)
        \end{rSubsection}
    \end{rSection}

    %----------------------------------------------------------------------------------------
    %	TECHNICAL PROJECTS SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Projects}
        \begin{rSubsection}{\textbf{Automated Taxonomy Construction}, Imperial College London} {Sep. 2013}{}{}
            \item Collaborated with Thomson Reuters, explored statistical approaches to automate terminology extraction
            and construction in large corpus, gained experience with multiple natural languages processing technologies
        \end{rSubsection}

        \begin{rSubsection}{\textbf{Research Assistant}, University of Liverpool} {Jul. 2012}{}{}
            \item Supported development of a European Framework Project in populating online reasoning framework (IMPACT),
            introduced innovative functionalities to the project, implemented initial prototype,
            and invited to deliver a keynote presentation to Chinese government officials in China-EU forum
        \end{rSubsection}
    \end{rSection}

    %----------------------------------------------------------------------------------------
    %	ADDITIONAL INFORMATION SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{ADDITIONAL INFORMATION}

        \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
            Languages & Native speaker of Mandarin Chinese, Fluent in English \\
            Tech Skills & Java, Python, SQL, JavaScript, MongoDB, Node.js   \\
            Hobbies & Swimming, Badminton, and Travelling  \\
        \end{tabular}

    \end{rSection}

    %----------------------------------------------------------------------------------------
    %	EXAMPLE SECTION
    %----------------------------------------------------------------------------------------

    %\begin{rSection}{Section Name}

    %Section content\ldots

    %\end{rSection}

    %----------------------------------------------------------------------------------------

\end{document}
